\HeaderA{boa.plot.geweke}{Plot Geweke Convergence Diagnostics}{boa.plot.geweke}
\keyword{hplot}{boa.plot.geweke}
\begin{Description}\relax
Creates a single plot of the Geweke convergence diagnostics within different 
line segments for a parameter in an MCMC sequence.
\end{Description}
\begin{Usage}
\begin{verbatim}
boa.plot.geweke(lname, pname, bins = boa.par("geweke.bins"), p.first = boa.par("geweke.first"), p.last = boa.par("geweke.last"), alpha = boa.par("alpha"), annotate = boa.par("legend"))
\end{verbatim}
\end{Usage}
\begin{Arguments}
\begin{ldescription}
\item[\code{lname}] Character string giving the name of the desired MCMC sequence in 
the working session list of sequences.
\item[\code{pname}] Character string giving the name of the parameter to be plotted.
\item[\code{bins}] Number of line segments within the MCMC sequence at which to plot 
the Geweke convergence diagnostics. The ith line segment contains the last 
((bins - i + 1) / bins)*100
bins. This may lead to segments in which there are too few iterations to 
compute the convergence diagnostics. Such segments, if they exist, are 
automatically omitted from the calculations.
\item[\code{p.first}] Proportion of iterations to include in the first window.
\item[\code{p.last}] Proportion of iterations to include in the last window.
\item[\code{alpha}] Alpha level for the rejection region lines drawn on the graph.
\item[\code{annotate}] Logical value indicating that a legend be included in the plot.
\end{ldescription}
\end{Arguments}
\begin{Value}
A logical value indicating that the plot was successfully created.
\end{Value}
\begin{Author}\relax
Brian J. Smith, Nicky Best, Kate Cowles
\end{Author}
\begin{SeeAlso}\relax
\code{\LinkA{boa.geweke}{boa.geweke}}, \code{\LinkA{boa.plot}{boa.plot}},
\code{\LinkA{boa.print.geweke}{boa.print.geweke}}
\end{SeeAlso}

