\HeaderA{boa.chain.info}{Information about MCMC Sequences}{boa.chain.info}
\keyword{utilities}{boa.chain.info}
\begin{Description}\relax
Returns summary information from a list of MCMC sequences.
\end{Description}
\begin{Usage}
\begin{verbatim}
boa.chain.info(chain, chain.support)
\end{verbatim}
\end{Usage}
\begin{Arguments}
\begin{ldescription}
\item[\code{chain}] List of matrices whose columns and rows contain the monitored
parameters and the MCMC iterations, respectively. The iteration numbers and
parameter names must be assigned to the dimnames.
\item[\code{chain.support}] List of matrices whose columns and rows contain the
monitored parameters and the support (lower and upper limits), respectively.
\end{ldescription}
\end{Arguments}
\begin{Value}
\begin{ldescription}
\item[\code{lnames}] Character vector giving the names of the MCMC sequences in the
session list of sequences.
\item[\code{pnames}] List of character vectors giving the parameter names in each
of the MCMC sequences.
\item[\code{iter}] List of numeric vectors giving the iterations from each MCMC
sequence.
\item[\code{iter.range}] Matrix whose columns give the range of the iterations for
the MCMC sequences named in the rows.
\item[\code{support}] List of numeric vectors giving the support for the parameters
in each of the MCMC sequences.
\end{ldescription}
\end{Value}
\begin{Author}\relax
Brian J. Smith
\end{Author}
\begin{SeeAlso}\relax
\code{\LinkA{boa.print.info}{boa.print.info}}
\end{SeeAlso}

