\HeaderA{boa.chain.import}{Import MCMC Sequence}{boa.chain.import}
\keyword{utilities}{boa.chain.import}
\begin{Description}\relax
Reads an MCMC sequence from an external file and adds it to the session lists
of sequences.
\end{Description}
\begin{Usage}
\begin{verbatim}
boa.chain.import(prefix, path = boa.par("path"), type = "ASCII")
\end{verbatim}
\end{Usage}
\begin{Arguments}
\begin{ldescription}
\item[\code{prefix}] Character string giving the prefix for the file(s) in which the
MCMC sequence is stored.
\item[\code{path}] Character string giving the directory path in which the file(s)
subsides.
\item[\code{type}] Character string specifying the type of data to be imported.
Currently, the supported types are:
\Itemize{
\item "ASCII" : ASCII text file. Calls \code{\LinkA{boa.importASCII}{boa.importASCII}} to import
data from "prefix.txt".
\item "BUGS" : BUGS output files. Calls \code{\LinkA{boa.importBUGS}{boa.importBUGS}} to import
data from "prefix.ind" and "prefix.out".
\item "S" : S data frame or matrix.
} 
\end{ldescription}
\end{Arguments}
\begin{Value}
A logical value indicating that the specified file(s) has been successfully imported.
\end{Value}
\begin{Section}{Side Effects}
The imported MCMC sequence is automatically added to the session lists of
sequences via a call to \code{\LinkA{boa.chain.add}{boa.chain.add}}.
\end{Section}
\begin{Author}\relax
Brian J. Smith
\end{Author}
\begin{SeeAlso}\relax
\code{\LinkA{boa.chain.add}{boa.chain.add}}, \code{\LinkA{boa.importASCII}{boa.importASCII}},
\code{\LinkA{boa.importBUGS}{boa.importBUGS}}
\end{SeeAlso}

